---
title: "F75 Project Final Report"
author: "DATA 550 Team"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
```

# Overview

This report is the reproducible scaffold for the F75 project. The repository is
organized so that data cleaning, figures, tables, and modeling live in separate
scripts under `code/`, while this report focuses on assembling and describing the
results.

# Workflow

The report is built by `make`, which runs the cleaning script, analysis modules,
and then renders this file. This structure supports clear task delegation across
team members and keeps the final document reproducible.

# Data

# Required Figure


# Required Table


# Additional Analyses

## Kaplan-Meier Curve

```{r, plot1}
knitr::include_graphics(
  here::here("output/figure/KM_plot_sex.png")
)
```

```{r, plot2}
knitr::include_graphics(
  here::here("output/figure/KM_plot_site.png")
)
```

```{r, plot3}
knitr::include_graphics(
  here::here("output/figure/KM_plot_bfeeding.png")
)
```

```{r, plot4}
knitr::include_graphics(
  here::here("output/figure/KM_plot_kwash.png")
)
```

```{r, plot5}
knitr::include_graphics(
  here::here("output/figure/KM_plot_hiv.png")
)
```

```{r, plot6}
knitr::include_graphics(
  here::here("output/figure/KM_plot_arm.png")
)
```

## Clinical Outcomes Table


## Regression Planning Output


## Supplementary EDA


# Team Notes

- Yixin Hu: longitudinal boxplots
- Helen Chen: Kaplan-Meier analysis and regression interpretation
- Sihang Jiang: summary tables and supplementary EDA
- Yuchen Li: regression modeling
- Project leader: workflow integration, output definitions, and final report assembly

