---
title: "F75 Project Final Report"
author: "Team: Yingpu (Paxton) Guo, Hua Xuan (Helen) Chen, Yuchen Li, Yixin Hu, Sihang Jiang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
```

# Overview

This report is the reproducible scaffold for the F75 project. The repository is
organized so that data cleaning, figures, tables, and modeling live in separate
scripts under `code/`, while this report focuses on assembling and describing the
results.

# Workflow

The report is built by `make`, which runs the cleaning script, analysis modules,
and then renders this file. This structure supports clear task delegation across
team members and keeps the final document reproducible.

# Data

# Required Figure


# Required Table


# Additional Analyses

## Kaplan-Meier Curves

Six Kaplan-Meier curves were constructed to analyze the time-to-stabilization (event being stabilization) for patients who did not experience deaths in the trial, stratified by the following variables: sex, study site, whether or not the child was breastfeeding at all, whether or not the child had Kwashiorkor (type of severe malnutrition), HIV status, and the randomization arm. 

From the plot below, we can see that the trajectories to stabilization are not statistically significantly different between males and females (p = 0.11). That being said, it appears that in general, males reached stabilization faster than females.

```{r, plot1}
knitr::include_graphics(
  here::here("output/figure/KM_plot_sex.png")
)
```

From the plot below, we can see that the trajectories to stabilization are not statistically significantly different between the 3 sites (p = 0.051), however, site B seems to have a generally faster time-to-stabilization compared to the other two sites.

```{r, plot2}
knitr::include_graphics(
  here::here("output/figure/KM_plot_site.png")
)
```

From the plot below, we can see that the trajectories to stabilization are generally similar between those still on breastfeeding and those who are not - they are not statistically significantly different (p = 0.29). That being said, in general, those who weren't on breastfeeding seem to have faster time-to-stabilization compared to those on breastfeeding. Perhaps age might be an interesting covariate to consider when explaining days to stabilization as the response, as those who are older wouldn't be on breastfeeding.

```{r, plot3}
knitr::include_graphics(
  here::here("output/figure/KM_plot_bfeeding.png")
)
```

From the plot below, we can see that the trajectories to stabilization are not statistically significantly different between those who had Kwashiorkor and those who didn't (p = 0.23). That being said, in general, those who didn't have Kwashiorkor appear to have faster time-to-stabilization compared to those who did have Kwashiorkor, suggesting that those who had this form of severe malnutrition took longer to achieve stabilization.

```{r, plot4}
knitr::include_graphics(
  here::here("output/figure/KM_plot_kwash.png")
)
```

From the plot below, we can see that the trajectories to stabilization are generally similar between those who were HIV positive, HIV negative, or had unknown HIV status - they are not statistically significantly different (p = 0.22). That being said, in general, we can see that those who were HIV- seemed to have faster time-to-stabilization compared to those who were HIV+. Since HIV affects the immune system, this trend is understandable.

```{r, plot5}
knitr::include_graphics(
  here::here("output/figure/KM_plot_hiv.png")
)
```

From the plot below, we can see that the trajectories to stabilization were not statistically significantly different between those who had the modified milk formula (intervention) compared to those who had the standard milk formula (p = 0.43). That being said, in general, those who were on the modifed milk formula appear to have faster time-to-stabilization compared to those who were on the standard formula. While this finding was not significant, it does suggest that the intervention could be effective in helping children reach stabilization faster, which could lead to better health outcomes.

```{r, plot6}
knitr::include_graphics(
  here::here("output/figure/KM_plot_arm.png")
)
```

## Clinical Outcomes Table


## Regression Planning Output

```{r}
### Logistic Regression Results (Discharged Status)

logit_results <- read.csv(
  here::here("output", "table", "logistic_regression_results.csv")
)

logit_results
```

From the logistic regression analysis, we were able to determine the correlation between the clinical and demographic factors and the probability of discharge.

Regarding the effect of the formula, the intervention (Modified F75) failed to have a significant effect compared to the other (standard F75) (p > 0.05), implying that there is no sufficient evidence to support the use of the modified formula for discharges.

The patient's HIV status had an interesting correlation with the discharge. The patients who did not have their HIV status determined had significantly low chances of being discharged than those whose HIV status was negative.

Age, gender, MUAC, and weight were not found to be significant factors in the prediction of discharge.

```{r}
### Linear Regression Results (Days Stable)

linear_results <- read.csv(
  here::here("output", "table", "linear_regression_results.csv")
)

linear_results
```

Factors correlated with number of days to stabilization have been identified from the linear regression analysis.

There were few predictors which proved to be statistically significant, hence indicating that these variables do not affect the time taken for stabilization in this data set.

Only one variable, kwashiorkor had some statistical significance (p-value was very close to 0.05) which indicated that those who had kwashiorkor took more days to get stabilized.

This suggests there may be some clinical significance in the result obtained but this needs to be studied with a large sample size to confirm the finding.

## Supplementary EDA


# Team Notes

- Yixin Hu: longitudinal boxplots
- Helen Chen: Kaplan-Meier analysis and regression interpretation
- Sihang Jiang: summary tables and supplementary EDA
- Yuchen Li: regression modeling
- Project leader: workflow integration, output definitions, and final report assembly

