---
title: "F75 Project Final Report"
author: "Team: Yingpu (Paxton) Guo, Hua Xuan (Helen) Chen, Yuchen Li, Yixin Hu, Sihang Jiang"
date: "`r Sys.Date()`"
output: html_document
params:
  regression_type: "both"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(here)
```

# Overview

This report is the reproducible scaffold for the F75 project. The repository is
organized so that data cleaning, figures, tables, and modeling live in separate
scripts under `code/`, while this report focuses on assembling and describing the
results.

# Workflow

The report is built by `make`, which runs the cleaning script, analysis modules,
and then renders this file. This structure supports clear task delegation across
team members and keeps the final document reproducible.

# Required Figure

The figure below shows the correlation structure among continuous clinical variables, including baseline anthropometric measurements, follow-up measurements, and days to stabilization.

```{r required-figure}
knitr::include_graphics(
  here::here("output/figure/heatmap_continuous.png")
)
```

The correlation heatmap provides an exploratory overview of the continuous-variable structure in the dataset. As expected, anthropometric measurements collected at related time points tended to show stronger positive relationships with one another, reflecting consistency across measures such as MUAC, weight, and height. By contrast, days to stabilization did not appear to be driven by a single dominant continuous variable, suggesting that stabilization time is likely multifactorial rather than strongly explained by one isolated measurement. Because the heatmap was generated from the cleaned analysis dataset, which excluded death-coded observations, it should be interpreted as reflecting patterns among participants with observed stabilization trajectories.

```{r, Figure1}
knitr::include_graphics(
  here::here("output/figure/height_boxplot.png")
)
```
For height, the comparison between baseline and discharge shows a modest upward shift in the distribution. While the median height increases slightly, the change is less pronounced than that observed for MUAC and weight. This is expected, as height is less sensitive to short-term nutritional interventions. The relatively stable spread of the data suggests that changes in height are limited over the study period.

```{r, Figure2}
knitr::include_graphics(
  here::here("output/figure/muac_boxplot.png")
)
```
From the boxplots of MUAC across baseline, stabilization, and discharge, we observe a clear upward trend in the distribution of MUAC over time. The median MUAC increases progressively from baseline to discharge, suggesting overall nutritional improvement during treatment. Additionally, the interquartile range (IQR) appears to shift upward, indicating that this improvement is consistent across a large proportion of patients. While some variability remains at each time point, the general pattern supports a positive response to the intervention.


```{r, Figure3}
knitr::include_graphics(
  here::here("output/figure/weight_boxplot.png")
)
```
The boxplots for weight show a similar increasing trend from baseline through stabilization to discharge. The median weight rises steadily, indicating that patients tend to gain weight during the treatment period. The spread of the data (IQR) also shifts upward, suggesting that weight gain is not limited to a small subset of patients but is observed broadly across the cohort. Although outliers are present, they do not substantially alter the overall pattern of weight improvement over time.


# Required Table
Baseline characteristics were summarized for the full study population by treatment group. Continuous variables were presented as mean (SD) or median (IQR), as appropriate, and categorical variables were presented as n (%).

```{r required-table}
knitr::kable(
  read.csv(here::here("output/table/table1_baseline.csv"))
)

```

Baseline characteristics were generally well balanced between the Standard F75 and Modified F75 groups, supporting a fair descriptive comparison of subsequent outcomes. The two treatment arms were nearly equal in size, and there were no obvious imbalances across age, sex, study site, caregiver relationship, breastfeeding status, or the major baseline anthropometric measures. Baseline MUAC, weight, and height appeared similar across groups, suggesting that the randomized arms were broadly comparable at study entry. Overall, these results indicate that any later differences in outcomes are less likely to be explained by major baseline differences alone.


## Kaplan-Meier Curves

Six Kaplan-Meier curves were constructed to analyze the time-to-stabilization (event being stabilization) for patients who did not experience deaths in the trial, stratified by the following variables: sex, study site, whether or not the child was breastfeeding at all, whether or not the child had Kwashiorkor (type of severe malnutrition), HIV status, and the randomization arm. 

From the plot below, we can see that the trajectories to stabilization are not statistically significantly different between males and females (p = 0.11). That being said, it appears that in general, males reached stabilization faster than females.

```{r, plot1}
knitr::include_graphics(
  here::here("output/figure/KM_plot_sex.png")
)
```

From the plot below, we can see that the trajectories to stabilization are not statistically significantly different between the 3 sites (p = 0.051), however, site B seems to have a generally faster time-to-stabilization compared to the other two sites.

```{r, plot2}
knitr::include_graphics(
  here::here("output/figure/KM_plot_site.png")
)
```

From the plot below, we can see that the trajectories to stabilization are generally similar between those still on breastfeeding and those who are not - they are not statistically significantly different (p = 0.29). That being said, in general, those who weren't on breastfeeding seem to have faster time-to-stabilization compared to those on breastfeeding. Perhaps age might be an interesting covariate to consider when explaining days to stabilization as the response, as those who are older wouldn't be on breastfeeding.

```{r, plot3}
knitr::include_graphics(
  here::here("output/figure/KM_plot_bfeeding.png")
)
```

From the plot below, we can see that the trajectories to stabilization are not statistically significantly different between those who had Kwashiorkor and those who didn't (p = 0.23). That being said, in general, those who didn't have Kwashiorkor appear to have faster time-to-stabilization compared to those who did have Kwashiorkor, suggesting that those who had this form of severe malnutrition took longer to achieve stabilization.

```{r, plot4}
knitr::include_graphics(
  here::here("output/figure/KM_plot_kwash.png")
)
```

From the plot below, we can see that the trajectories to stabilization are generally similar between those who were HIV positive, HIV negative, or had unknown HIV status - they are not statistically significantly different (p = 0.22). That being said, in general, we can see that those who were HIV- seemed to have faster time-to-stabilization compared to those who were HIV+. Since HIV affects the immune system, this trend is understandable.

```{r, plot5}
knitr::include_graphics(
  here::here("output/figure/KM_plot_hiv.png")
)
```

From the plot below, we can see that the trajectories to stabilization were not statistically significantly different between those who had the modified milk formula (intervention) compared to those who had the standard milk formula (p = 0.43). That being said, in general, those who were on the modifed milk formula appear to have faster time-to-stabilization compared to those who were on the standard formula. While this finding was not significant, it does suggest that the intervention could be effective in helping children reach stabilization faster, which could lead to better health outcomes.

```{r, plot6}
knitr::include_graphics(
  here::here("output/figure/KM_plot_arm.png")
)
```

## Clinical Outcomes Table

Clinical outcomes were summarized by treatment group using the full sample. Values coded as 999 for `days_stable` were treated as death codes rather than numeric stabilization times when summarizing time to stabilization.

```{r clinical-outcomes-cat}
knitr::kable(
  read.csv(here::here("output/table/table2_outcomes_cat.csv"))
)

knitr::kable(
  read.csv(here::here("output/table/table2_outcomes_days.csv"))
)
```

Clinical outcomes did not suggest a clear descriptive advantage of Modified F75 over Standard F75. In-hospital death remained a notable outcome overall, and the Standard F75 group showed slightly lower mortality and slightly higher successful discharge than the Modified F75 group. Reached stabilization was common in both arms, although the Standard F75 group appeared to have a modestly higher proportion of participants who stabilized, while failure to stabilize before death or withdrawal was somewhat more frequent in the Modified F75 group. Importantly, among participants with observed stabilization times, the median days to stabilization was the same in both treatment groups, indicating no meaningful difference in stabilization speed at the level of simple summary statistics. In this analysis, values coded as 999 for days_stable were treated as death codes rather than true numeric times, which was an appropriate choice for outcome summarization.

```{r logistic-header, eval = params$regression_type %in% c("both", "logistic"), results='asis'}
cat("## Logistic Regression Results (Discharged Status)\n")
```

```{r logistic-results, eval = params$regression_type %in% c("both", "logistic")}
logit_results <- read.csv(
  here::here("output", "table", "logistic_regression_results.csv")
)
logit_results
```

```{r logistic-text, eval = params$regression_type %in% c("both", "logistic"), results='asis'}
cat("From the logistic regression analysis, we were able to determine associations between the clinical and demographic factors and the probability of discharge.

The intervention (Modified F75) was not statistically significantly associated with discharge status, so there's insufficient evidence of a difference between the intervention and the standard formula in predicting patient discharge status, holding all else constant.

A patient's HIV status had an interesting association with the discharge status. Patients who had an unknown HIV result had significantly lower chances of being discharged compared to those who had negative HIV status (p = 0.04), holding all else constant.

Age, gender, MUAC, and weight were not found to be significant predictors of discharge status.
")
```

```{r linear-header, eval = params$regression_type %in% c("both", "linear"), results='asis'}
cat("## Linear Regression Results (Days Stable)\n")
```

```{r linear-results, eval = params$regression_type %in% c("both", "linear")}
linear_results <- read.csv(
  here::here("output", "table", "linear_regression_results.csv")
)
linear_results
```

```{r linear-text, eval = params$regression_type %in% c("both", "linear"), results='asis'}
cat("None of the covariates were statistically significantly associated with days to stabilization. While the variables were not statistically significant, there could be clinical significance or relevance for including them in a model.

The intervention (Modified F75) was not significantly associated with days to stabilization, so there's insufficient evidence of a difference between the intervention and the standard formula in explaining days to stabilization, holding all else constant.
")
```

## Supplementary EDA

Scatterplots involving days to stabilization were restricted to participants with observed stabilization times, because death-coded values are not interpretable as continuous follow-up times. Representative plots are shown below.

```{r}
knitr::include_graphics(
  here::here("output/figure/scatter_muac_days_stable.png")
)
knitr::include_graphics(
  here::here("output/figure/scatter_weight_days_stable.png")
)
knitr::include_graphics(
  here::here("output/figure/scatter_height_days_stable.png")
)
```

The scatterplots were useful for exploratory assessment of the relationship between selected continuous predictors and days to stabilization. These figures were restricted to participants with observed stabilization times, since death-coded values are not interpretable as continuous follow-up times. Across the displayed plots, the relationships with days to stabilization appeared modest rather than strongly linear, with no single variable showing a clear, dominant pattern. Accordingly, these scatterplots are best interpreted as descriptive visual checks for trend, spread, and possible outliers rather than as formal evidence of strong single-variable associations. Representative plots were shown in the report, while the broader goal of this section was to assess whether any continuous variables displayed obvious relationships with stabilization time.

Overall, the two treatment groups appeared broadly comparable at baseline. In the descriptive outcome summaries, the Standard F75 group showed slightly lower mortality and slightly higher successful discharge and stabilization rates, while median days to stabilization was the same in both groups. The heatmap and scatterplots were useful for exploratory assessment of continuous-variable relationships, but they did not suggest a strong single-variable explanation for time to stabilization.

# Team Notes

- Yixin Hu: longitudinal boxplots
- Helen Chen: Kaplan-Meier analysis and regression interpretation
- Sihang Jiang: summary tables and supplementary EDA
- Yuchen Li: regression modeling
- Project leader: workflow integration, output definitions, and final report assembly

